LAGOS lake depth

### 2020-01-01 figures/00_cutoffs.Rmd
add figure description

```{r 00_cutoffs, echo=FALSE, message=FALSE, eval=TRUE, warning=FALSE, results='hide'}
lg <- lagosus_load("locus")
dt <- read.csv("../data/lagosus_depth.csv", stringsAsFactors = FALSE) %>%
  dplyr::select(lagoslakeid, lake_maxdepth_m)

>>>>

```{r 00_cutoffs, echo=FALSE, message=FALSE, eval=TRUE, warning=FALSE, results='hide'}
# proportion max depth availability by lake area class
lg <- lagosus_load("locus")
dt <- read.csv("../data/lagosus_depth.csv", stringsAsFactors = FALSE) %>%
  dplyr::select(lagoslakeid, lake_maxdepth_m)
